---
title: "Supporting data for the MutSeqR package"
author:
- name: Annette E. Dodge
- name: Matthew J. Meier
  email: matthew.meier@hc-sc.gc.ca
Date: "`r Sys.Date()`"
package: MutSeqRData
output:
  BiocStyle::html_document
abstract: |
  Description of your vignette
vignette: |
  %\VignetteIndexEntry{SUpporting data for the MutSeqR package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# MutSeqRData

This data package provides supporting data for [MutSeqR](https://github.com/EHSRB-BSRSE-Bioinformatics/MutSeqR).

This package contain the following objects:
  - Example import_mut_data
  - Example import_mut_data using Custom column names
  - Example import_vcf_data
  - Example mutation data
  - Example mutation data filtered
  - Precalculated Depth at Base 6 Resolution
  - Precalculated Depth at Base 12 Resolution
  - Precalculated Depth at Base 96 Resolution
  - Precalculated Depth at Base 192 Resolution


# Installation

Install MutSeqRData from Bioconductor:

```{r, eval = FALSE}
if (!require("BiocManager", quietly=TRUE)) {
  install.packages("BiocManager")
}
BiocManager::install("MutSeqRData")
```

Or from Github:

```{r, eval = FALSE}
if (!require("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("EHSRB-BSRSE-Bioinformatics/MutSeqRData")
```

Load the package:

```{r, eval = FALSE}
library(MutSeqRData)
```

# Access Data from ExperimentHub

```{r, eval = FALSE}
if (!require("BiocManager", quietly=TRUE)) {
  install.packages("BiocManager")
}
if (!require("ExperimentHubData", quietly = TRUE)) {
  BiocManager::install("ExperimentHubData")
}
library(ExperimentHub)
eh <- ExperimentHub()
query(eh, "MutSeqRData")
mutation_data <- eh[["access # here"]]

```

# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
